---
title: "Regression"
author: "Julio Lopez"
date: "`r Sys.Date()`"
output: 
  html_document: 
    highlight: pygments
    theme: cerulean
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Regression example

## Simple text

This is a simple, bivariate regression example.
Two plus two equals `r 2 + 2`.


```{r, math_example}
2 + 2
```

Puedes poner TRUE or FALSE para mostrar codigo o no. O mensajes de warning.
```{r, my_setup, echo=TRUE, message=FALSE}
library(languageR)
library(tidyverse)
str(spanish)
```

## Tidy some data

Here we tidy the data. Este codigo sirve para manipular el tamaño del grafico. Me puede servir para los graficos del QP.

```{r, my_plot, fig.align='center', fig.width=5, fig.height=5}
my_data <- spanish %>%
  select(., x = X14461gll, y = X14473gll) %>%
  filter(., y < 0.06, x < 0.075)

my_data %>%
  ggplot(., aes(x = x, y = y)) +
  geom_point() + 
  geom_smooth(method = 'lm')
```

## Model

Here we fit a model.

```{r, my_model}
my_fit <- lm(y ~ x, data = my_data)
summary(my_fit)
```

confint te dice confidence intervals
```{r}
confint(my_fit)
```
The data xxxxxxxx (CI: LB: `r confint(my_fit)[1.2]`)

coefficients es para coefficients
```{r}
coefficients(my_fit)
```
Slope: `r coefficients(my_fit)[2]` , CI: LB: `r round(confint(my_fit)[1, c(1,2)], 3)`)

```{r}
# test normality of residuals
hist(residuals(my_fit))
qqnorm(residuals(my_fit))
qqline(residuals(my_fit))
```

# my new model

# simple silly text
```{r}
data1 <- spanish %>%
  select(., x = X14466gll, y = X14459gll)

data1 %>%
  ggplot(., aes(x = x, y = y)) +
  geom_point() + 
  geom_smooth(method = 'lm')

# fit
fit1 <- lm(y ~ x, data = data1)
summary(fit1)

# CI
confint(fit1)

# Coef
coefficients(fit1)
```